<<<<<<< HEAD
# Similarity comparisons


## Comparison four distance mDag eukaryote

Load the similarities for  pairs and comparison

```{r}
library(gtools)

n=length(meta_taxo$mDAG_Id)
dim(dis_DirectedMethod)
aux1=base::rep(x=1:n,each=c(n:1))

aux=as_tibble(dis_DirectedMethod)
aux$mDag=names(aux)
aux=aux %>% pivot_longer(cols=`0089`:`0038`,names_to="mDag_2",values_to="dis_Direct")
aux_2= aux %>%  mutate(i=pmax(as.integer(mDag),as.integer(mDag_2)),j=pmin(as.integer(mDag),as.integer(mDag_2))) %>% unite("ij",i:j) %>% filter(duplicated(ij))

aux=as_tibble(dis_MunkrestMethod)
aux$mDag=names(aux)
aux=aux %>% pivot_longer(cols=`0089`:`0038`,names_to="mDag_2",values_to="dis_Munkrest")
aux_2 = aux_2 %>% left_join(aux)

aux=as_tibble(dis_DirectMethod_MunkrestMethod)
aux$mDag=names(aux)
aux=aux %>% pivot_longer(cols=`0089`:`0038`,names_to="mDag_2",values_to="dis_Direct_Munkrest")
aux_2 = aux_2 %>% left_join(aux)

aux=as_tibble(dis_MunkrestMethod_DirectMethod)
aux$mDag=names(aux)
aux=aux %>% pivot_longer(cols=`0089`:`0038`,names_to="mDag_2",values_to="dis_Munkrest_Direct")
aux_2 = aux_2 %>% left_join(aux)
dis=aux_2[,c(1,2,4,3,5:7)]
rm(aux,aux_2)
```

**Tablas de las correlaciones de Speramen y Pearson entre las 4 distancias.**

```{r}
cor(dis[,4:7],method="spearman")



cor(dis[,4:7],method="pearson")
```

```{r}
knitr::include_graphics(
  c("data_medag_20230321_long_report_03042023_files/figure-html/unnamed-chunk-3-1.png",
    "data_medag_20230321_long_report_03042023_files/figure-html/unnamed-chunk-4-1.png",
    "data_medag_20230321_long_report_03042023_files/figure-html/unnamed-chunk-13-1.png",
    "data_medag_20230321_long_report_03042023_files/figure-html/unnamed-chunk-14-1.png",
    "data_medag_20230321_long_report_03042023_files/figure-html/unnamed-chunk-23-1.png",
    "data_medag_20230321_long_report_03042023_files/figure-html/unnamed-chunk-24-1.png",
    "data_medag_20230321_long_report_03042023_files/figure-html/unnamed-chunk-33-1.png",
    "data_medag_20230321_long_report_03042023_files/figure-html/unnamed-chunk-34-1.png"))
```

```{r}
library(GGally)
ggpairs(dis[,4:7])
```

```{r}
boxplot(dis[,4:7])



```
=======
# Distances comparisons 

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,warning = FALSE,echo=FALSE,message=FALSE)
```

# Comparison four distance mDag eukaryote

```{r}
library(tidyverse)
load("four_dist_meta_taxo.Robj")
library(gtools)
n=length(meta_taxo$mDAG_Id)
dim(dis_DirectedMethod)
aux1=base::rep(x=1:n,each=c(n:1))

aux=as_tibble(dis_DirectedMethod)
aux$mDag=names(aux)
aux=aux %>% pivot_longer(cols=`0089`:`0038`,names_to="mDag_2",values_to="dis_Direct")
aux_2= aux %>%  mutate(i=pmax(as.integer(mDag),as.integer(mDag_2)),j=pmin(as.integer(mDag),as.integer(mDag_2))) %>% unite("ij",i:j) %>% filter(duplicated(ij))

aux=as_tibble(dis_MunkrestMethod)
aux$mDag=names(aux)
aux=aux %>% pivot_longer(cols=`0089`:`0038`,names_to="mDag_2",values_to="dis_Munkrest")
aux_2 = aux_2 %>% left_join(aux)

aux=as_tibble(dis_DirectMethod_MunkrestMethod)
aux$mDag=names(aux)
aux=aux %>% pivot_longer(cols=`0089`:`0038`,names_to="mDag_2",values_to="dis_Direct_Munkrest")
aux_2 = aux_2 %>% left_join(aux)

aux=as_tibble(dis_MunkrestMethod_DirectMethod)
aux$mDag=names(aux)
aux=aux %>% pivot_longer(cols=`0089`:`0038`,names_to="mDag_2",values_to="dis_Munkrest_Direct")
aux_2 = aux_2 %>% left_join(aux)
dis=aux_2[,c(1,2,4,3,5:7)]
rm(aux,aux_2)
```

**Tablas de las correlaciones de Speramen y Pearson entre las 4 distancias.**

```{r}
cor(dis[,4:7],method="spearman")



cor(dis[,4:7],method="pearson")
```

```{r}
knitr::include_graphics(
  c("data_medag_20230321_long_report_03042023_files/figure-html/unnamed-chunk-3-1.png",
    "data_medag_20230321_long_report_03042023_files/figure-html/unnamed-chunk-4-1.png",
    "data_medag_20230321_long_report_03042023_files/figure-html/unnamed-chunk-13-1.png",
    "data_medag_20230321_long_report_03042023_files/figure-html/unnamed-chunk-14-1.png",
    "data_medag_20230321_long_report_03042023_files/figure-html/unnamed-chunk-23-1.png",
    "data_medag_20230321_long_report_03042023_files/figure-html/unnamed-chunk-24-1.png",
    "data_medag_20230321_long_report_03042023_files/figure-html/unnamed-chunk-33-1.png",
    "data_medag_20230321_long_report_03042023_files/figure-html/unnamed-chunk-34-1.png"))
```

```{r}
library(GGally)
ggpairs(dis[,4:7])
```

```{r}
boxplot(dis[,4:7])



```
>>>>>>> 67440c1f760214cc7671eb39b3e6e8b809275dc2
