```{r  include=FALSE,message=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      cache=FALSE,
                      warning = FALSE,
                      message = FALSE, out.width = "100%",cache.lazy=FALSE)
pdf="TRUE"

library(tidyverse)
library(igraph)
library(ComplexHeatmap)
library(viridis)
library(circlize)
library(plotly)
library(randomcoloR)
library(factoextra)
library(RColorBrewer)
library(kableExtra)
library(igraph)
library(GGally)
```

```{r}
gc()
load(file='metadag_work_space.RData')
gc()
```

# Metabolic Graphs

We present here some analysis examples of the metabolic graphs generated in GraphML format.

## Metabolic graphs for each organism

Read the individual metabolic graphs generated for Homo sapiens (KEGG id: hsa) in the directory(Individuals/hsa)

```{r}
experiment=
  "0a845f74-826e-3b46-aed9-e7ecf74db262/"
path_exp=paste0("data/",experiment)
files_hsa=dir(paste0(path_exp,"Individuals/hsa"))
files_hsa
```

```{r echo=FALSE}
files_hsa=dir(paste0(path_exp,"Individuals/hsa"))
# "plot mDAG pdf format",
#             "plot mDAG svg format",
type_file=c("m-DAG GraphML format",
            "m-DAG pdf graphic",
            "m-DAG svg graphic",
            "csv file with the adjacency matrix of the m-DAG",
            "pdf graphic with the biggest conected component of the m-DAG",
            "svg graphic with the biggest conected component of the m-DAG ",
            "csv file with the node (MBBs) labels  of the m-DAG", 
            "csv file with all connected components of the m-DAG",
            "csv file with the  adjacency matrix of the reaction graph",
            "csv file with the node (reactions) labels  of the reaction graph", 
            "reaction graph  GraphML format",
            "reaction graph pdf graphic",
            "reaction graph svg graphic",
            "text summary file with the number of MBBs, reactions, etc. in the previous graphs"
)
knitr::kable(data.frame(files_Individual_hsa=files_hsa, Description=type_file))
```

## Pan & core metabolic graphs

Pan and core metabolic graphs for every group were generated. For instance, one can read the pan and core metabolic graphs generated for the group Algae in the directory (Groups/Algae).

```{r}
files_Algae=dir(paste0(path_exp,"Groups/Algae"))
files_Algae
```

The global core reaction graph, which is the core of all the organisms' reaction graphs in this Eukaryotes test, is empty.

```{r graph_core_ALL}
graph_core_RC=read.graph(
  paste0(path_exp,
         "Global/core/core_RC.graphml"),
  format = "graphml")
summary(graph_core_RC)
```

The global core reaction graph has `r igraph::vcount(graph_core_RC)` vertex and `r igraph::ecount(graph_core_RC)` edges. It is an empty graph.

The core reaction graph for the Algae group is:

```{r fig.cap="Algae core reaction graph"}
knitr::include_graphics(
  paste0(path_exp,"Groups/MSA_Cluster_3/core/MSA_Cluster_3_core_RC.pdf"))
```

The global core m-DAG, i.e., the core of all organisms in this example is empty.

```{r}
graph_core_mDAG=read.graph(
  paste0(path_exp,"Global/core/core_mDAG.graphml"),
  format = "graphml")
summary(graph_core_mDAG)
```

The global core m-DAG has `r igraph::vcount(graph_core_mDAG)` vertex and `r igraph::ecount(graph_core_mDAG)` edges. It is an empty graph.

The core metabolic DAG for the Algae group is:

```{r fig.cap="Core m-DAG for Algae"}
knitr::include_graphics(paste0(path_exp,                              "Groups/Algae/core/Algae_core_mDAG.pdf"))
```

The global pan reaction graph for the Animals Kingdom is:

```{r}
graph_pan_RC=read.graph(
  paste0(path_exp,
         "TaxonomyLevels/Kingdom/Animals/pan/Animals_pan_RC.graphml"),
  format = "graphml")
summary(graph_pan_RC)
```

This pan reaction graph has `r igraph::vcount(graph_pan_RC)` nodes and `r igraph::ecount(graph_pan_RC)` edges.

## Graph's topology

From the GraphML files, one can extract topological information. Some examples are as follows.

The diagram below illustrates the distribution of node degrees for an m-DAG.

```{r}
graph_mDAG=read.graph(
  paste0(path_exp,
         "Individuals/hsa/hsa_mDAG.graphml"),
  format= "graphml")
summary(graph_mDAG)
barplot(table(igraph::degree(graph_mDAG,mode="all")),
        ylim=c(0,350),col="blue",
        main="Frequency of Node Degrees",
        ylab="Frequency",xlab="Degree")
```

The connected components of every graph as well as the size of every connected component can be obtained as:

```{r}
compo=components(graph_mDAG,mode = "weak")
str(compo)
compo$csize
k=which.max(compo$csize==max(compo$csize))
k
table(compo$membership)
vertex=which(compo$membership==k)
length(vertex)
Big_Component=induced_subgraph(graph_mDAG, vids=vertex)
igraph::vcount(Big_Component)
igraph::ecount(Big_Component)
```

And the plot of the bigger component of the m-DAG in Homo sapiens is:

```{r fig.align='center',title="Bigger component of hsa mDAG"}
knitr::include_graphics(paste0(path_exp,
                               "Individuals/hsa/hsa_mDAG_biggerDAG.pdf"))
```

```{r}
#path_exp="data/result_bb261b6e-95c6-3e39-b82b-b68eea80e30b/data/" 
list_names=dir(paste0(path_exp,"Individuals/"))
list_names= list_names[-1] # filter 0000_RefPw
length(list_names) 
graphs_list=paste0(path_exp,"Individuals/", list_names,"/",list_names, "_MDAG.graphml")
```

```{r}
knitr::include_graphics(
  paste0(path_exp,"Individuals/cang/cang_RC.pdf"))
```

## Graph statistics

The number of connected component in each generated m-DAG with their frequency in the entire set of m-DAGs, can be obtained as follows:

```{r ,warning=FALSE}
read_mDAG=function(x) {DAG=read.graph(file=x,
                                      format="graphml")
return(DAG)}
mDAG_components=function(x) {
  sort(components(x,mode = "weak")$csize,
       decreasing=TRUE)
}

compo_list=lapply(graphs_list,
                  FUN=function(x) {
                    gg=read_mDAG(x)
                    aux=list(
                      mDAG_components=mDAG_components(gg),
                      degree_count=igraph::degree(gg,mode="total"))
                    return(aux)}
)

names(compo_list)=list_names
n=max(sapply(compo_list,FUN=function(x) {length(x[[1]])}))
n
size_compo_list=lapply(compo_list,FUN=function(x) {
  return(c(x[[1]],rep(NA,n-length(x[[1]]))))})

aux=do.call(bind_cols,size_compo_list)
weak_components_size=pivot_longer(aux,aaf:zvi,names_to="Organism",
                                 values_to="csize") %>% 
  arrange(Organism,-csize)
weak_components_size$index=rep(1:n,times=dim(aux)[2])
weak_components_size=weak_components_size %>%
  left_join(meta_taxo,by="Organism") %>% filter(!is.na(Kingdom),!is.na(csize))
weak_components_size_raw=weak_components_size
```

```{r ,warning=FALSE,cache=FALSE}
Organism=names(compo_list)

size_MBB=function(org){
  #org="hsa"
  x=Results %>% filter(Organism==org) %>% select(!contains("_rev"))
  x=as.character(x[1,6:dim(x)[2]])
  x=x[(!is.na(x))]
  x=x[x!="NA"]
  tt=data.frame(sort(table(x),decreasing=TRUE),org)
  names(tt)=c("MBB","size","Organism")
  return(tt)
}


size_list_raw= lapply(Organism,FUN=function(x) size_MBB(x))
names(size_list_raw)=Organism
```

Kingdom=weak_components_size\$Kingdom

```{r ,warning=FALSE,cache=FALSE}
size_MBB_df=do.call(rbind,size_list_raw)
max(size_MBB_df$size)

size_MBB_df=size_MBB_df %>% left_join(meta_taxo%>% select(Organism,Kingdom),by="Organism") %>% filter(!is.na(Kingdom))
```

We can visualize the sizes of the weak components for each m-DAG, using colors to represent the different Kingdoms, also we scale the results by a log-log plot:

```{r}
COLOR_KINGDOM=c("red","yellow","green","black")
colors_kingdom=weak_components_size%>% select(Organism,Kingdom) %>% distinct()
names(COLOR_KINGDOM)=sort(unique(colors_kingdom$Kingdom))

p1<- ggplot(data=weak_components_size) + 
  geom_line(mapping=aes(x=index,
                        y=csize,group = Organism,
                        color=Kingdom),
            na.rm=TRUE) + 
  scale_x_continuous(trans="identity") + 
  scale_y_continuous(trans="identity") +
  ylim(0,640)+
  ggtitle("Plot of weak components size decreasing order.")+
  ylab("Weak components size") + xlab("Order")+
  scale_color_manual(values =COLOR_KINGDOM[colors_kingdom$Kingdom])

p2<- ggplot(data=weak_components_size) + 
  geom_line(mapping=aes(x=index,
                        y=csize,group = Organism,
                        color=Kingdom),
            na.rm=TRUE) + 
  scale_y_continuous(trans='log10') + 
  scale_x_continuous(trans='log10') +
  scale_color_manual(values =COLOR_KINGDOM[colors_kingdom$Kingdom])+
  ggtitle("Plot log10-log10 of size  weak components decreasing order.") +
  ylab("Log10 weak component size") + xlab("Log10 order")
p1
p2
```

A table with the frequencies of the weak connected components sizes, displayed by Kingdom, can be obtained as follows:

```{r}
aux=table(weak_components_size$csize,weak_components_size$Kingdom)
table_wcc_size=tibble(Order=1:dim(aux)[1],
                      Wcc_size=as.integer(unlist(dimnames(aux)[1])),
                      Animals=aux[,1],
                      Fungi=aux[,2],
                      Plants=aux[,3],
                      Protists=aux[,4])
knitr::kable(table_wcc_size)%>% kable_styling(bootstrap_options = "striped", full_width = FALSE) %>%
  scroll_box(height = "300px", width = "100%")
```

A table with the frequencies of the MBBs sizes displayed by Kingdom can be obtained as follows:

```{r}
size_MBB_df_table= size_MBB_df %>% group_by(Kingdom,size) %>% summarise(n=n())

table_MBB_size = size_MBB_df_table %>% pivot_wider(names_from = Kingdom, values_from = n, values_fill = list(n = 0)) %>% arrange(size)
knitr::kable(table_MBB_size)%>% kable_styling(bootstrap_options = "striped", full_width = FALSE) %>% scroll_box(height = "300px", width = "100%")
```

```{r include=FALSE}
write_csv(table_MBB_size,"table_MBB_size.csv")
```

```{r pasar_load, include=FALSE}
save.image(file='metadag_work_space.RData')
```

### More statistics

h

```{r}

weak_components_size$Kingdom <- factor(weak_components_size$Kingdom)
#weak_components_size


g <- ggplot(weak_components_size) +
  xlab("") +  # Eliminar el título del eje X
  ylab("Size of connected component") +  # Etiqueta del eje Y
  geom_jitter(aes(x = Kingdom, y = csize, color = Kingdom),
             size = 1) +  # Colorear puntos según 'Kingdom' y reducir el tamaño
  scale_y_continuous(breaks = seq(0, 640, by = 100)) +  # Escala del eje Y con saltos de 20
  theme_minimal() + # Tema minimalista con fondo blanco
  ggtitle("")  # Título del gráfico
  g

```

```{r}
weak_components_size_max = weak_components_size %>%
  group_by(Organism) %>%
  summarise(csize = max(csize),Kingdom=first(Kingdom))
# Crear el gráfico de violín con puntos jitter
g <- ggplot(weak_components_size_max, aes(x = Kingdom, y = csize)) +
  geom_violin(aes(fill = Kingdom), trim = FALSE, alpha = 0.5) +  # Gráfico de violín con relleno por 'Kingdom' y sin recortar
  geom_jitter(aes(color = Kingdom), size = 1, width = 0.2) +  # Puntos con jitter para evitar solapamientos
  xlab("") +  # Eliminar el título del eje X
  ylab("Size of biggest connected component") +  
  scale_y_continuous(breaks = seq(0, 640, by = 100)) +  
  theme_minimal() +  # theme background white
  ggtitle("")  #
#Size of the largest weakly connected component by Kingdom \n (Violin Plot with Jittered Points)
# Mostrar el gráfico
g
```
